---
title: "Report diagnostics"
output: 
  html_document:
    toc: true
    toc_float: true
    depth: 2
params:
  run: "001"
  logDV: FALSE
  modelDir: !r here::here("model/pk")
  script: "template-bayes-report.Rmd"
  yspec: "analysis3.yml"
  contCov: !r c("AGE","WT","ALB","EGFR")
  catCov: !r c("STUDY", "RF", "CP", "DOSE")
  etas: !r c("ETA1//ETA-KA", "ETA2//ETA-V/F", "ETA3//ETA-CL/F")
  include_code: FALSE
  include_plots: TRUE
# sims_output_path: either of
#   1. path of RDS file containing simulated output (EPRED, IPRED, EWRES, NPDE)
#   2. "" to use only NONMEM output
  sims_output_path: ""
  #sims_output_path: !r here::here("model/nonmem/pk/001/diag-sims-001.rds")
# plot_ci: if true, include CIs on DV vs prediction plots (only relevant when sims_output_path is not "")
  plot_ci: FALSE
# TODO infer from dirs
  n_chains: 4
# n_thin: select every `n_thin` samples for trace/density plots (from ctl - 4000 niters)
  n_thin: 10
# n_thin2: select every `n_thin * n_thin2` samples for Bayes pairs plots (from ctl - 4000 niters)
  n_thin2: 1
# theta_cov: indices of covariate ETAs to separate when creating pairs plots, e.g. !r c(1, 2, 6)
#   set to NULL to create a single pairs plot
  theta_cov: NULL
#  theta_cov: !r c(6, 7, 8)
  tbl_offdiag: TRUE
  plot_offdiag: TRUE
  run_mrggsave: TRUE
---

# Run number `r params$run`

# Purpose

To produce a set of diagnostic plots that will be included in the report. Please note
that these plots are just meant to provide an example of what could be created and how. 
They are not an exhaustive list of every possible plot and were chosen with the project 
aims in mind. 

While this _should_ give users examples of plots generated with the most up-to-date 
packages and methods, we're always happy to have feedback. If you know of more 
efficient methods or want to suggest alternative ways of plotting the figures 
please open an issue with the details. 


# Set up

```{r setup_general, include = F}
### General script set-up
knitr::opts_chunk$set(
  echo = TRUE, 
  warning = FALSE, 
  message = FALSE,
  fig.height = 5, 
  fig.width = 5
)

### Libraries ----------------------------
suppressPackageStartupMessages(library(tidyverse))
library(pmplots)
library(bbr)
library(PKPDmisc)
library(yaml)
library(yspec)
library(mrggsave)
library(pmtables)
library(mrgsolve)
library(furrr)
#library(npde)
library(patchwork)
library(loo)
suppressPackageStartupMessages(library(rstan))
suppressPackageStartupMessages(library(glue))
suppressPackageStartupMessages(library(cowplot))
# use_bbi(.version = "v3.1.0") ## << need this version to run this script
# bbi_version()

# added this because npde imports mclust (which uses its own map())
#map <- purrr::map

### Directories ----------------------------
figDir <- here::here("deliv", "figure","report")
tabDir <- here::here("deliv", "table","report")
dataDir <- here::here("data")
sourceDataDir <- file.path(dataDir, "source")
derivedDataDir <- file.path(dataDir, "derived")

#if (!file.exists(figDir)) dir.create(figDir)
#if (!file.exists(tabDir)) dir.create(tabDir)

thisScript <- params$script
options(mrg.script = params$script,
  mrggsave.dev = "pdf,png")

theme_set(pmplots::pm_theme())

if (params$sims_output_path != "") {
  if (!file.exists(params$sims_output_path)) {
    stop(glue("File {params$sims_output_path} does not exist"))
  } else {
    sims <- readRDS(params$sims_output_path)
  }
}
if (params$plot_ci & params$sims_output_path == "") {
  stop("Set `sims_output_path` (after running simulations) in order to plot CIs")
}
```


```{r load_any_functions, include = F}
### Source function scripts
source(here::here("script/functions-diagnostics-npde.R"))
source(here::here("script/functions-diagnostics-rhat-ess.R"))
source(here::here("script/functions-model.R")) # need this for the `redataset` function
```

```{r desc_test, include = F}
# Descriptive text that depends on the settings used for diagnostic simulations
# (and whether diagnostic simulations were run at all)

ind_pred_text <- glue(
  "Individual predictions are medians of the values of IPRED output by NONMEM
  for each of the {params$n_chains} chains."
)
etas_text <- glue(
  "ETAs are medians of the values
  of ETA output by NONMEM for each of the {params$n_chains} chains."
)
if (params$sims_output_path == "") {
  
  # Medians of NONMEM output only
  pop_pred_text <- glue(
    "Population predictions are medians of the values of EPRED output by NONMEM
    for each of the {params$n_chains} chains."
  )
  dv_pred_text <- glue(pop_pred_text, ind_pred_text, .sep = " ")
  npde_text <- glue(
    "Normalized prediction distribution errors (NPDE) are medians of the values
    of NPDE output by NONMEM for each of the {params$n_chains} chains."
  )
  ewres_text <- glue(
    "Expected weighted residuals (EWRES) are medians of the values
    of EWRES output by NONMEM for each of the {params$n_chains} chains."
  )
  
} else {
  
  # Medians (and optionally upper/lower percentiles) from simulations
  pop_pred_text <- glue(
    "Population predictions are medians of {sims$n_post} simulated values
    incorporating between-{ifelse(sims$resid_var, ' and within-', '')}subject
    variability, as well as uncertainty in population parameter estimates via
    sampling from the posterior distribution."
  )
  if (sims$ipred_sim) {
    ind_pred_text <- glue(
      "Individual predictions are medians of {sims$n_post} simulated values
      incorporating conditional estimates of individual parameters and include
      {ifelse(sims$resid_var, 'within-subject variability, as well as', '')}
      uncertainty in population parameter estimates via sampling from the
      posterior distribution."
    )
    etas_text <- glue(
      "ETAs are medians of {sims$n_post} posterior ETAs across
      the {params$n_chains} chains."
    )
  }
  dv_pred_text <- glue(pop_pred_text, ind_pred_text, .sep = " ")
  if (params$plot_ci) {
    dv_pred_text <- glue(
      dv_pred_text,
      " Red error bars represent {sims$ci_level}% CIs."
    )
  }
  npde_text <- glue(
    "Normalized prediction distribution errors (NPDE) are Monte-Carlo generated
    diagnostics, using {sims$n_post} simulations incorporating
    between-{ifelse(sims$resid_var, ' and within-', '')}subject variability,
    as well as uncertainty in population parameter estimates via
    sampling from the posterior distribution."
  )
  ewres_text <- glue(
    "Expected weighted residuals (EWRES) are Monte-Carlo generated residuals,
    using {sims$n_post} simulations incorporating
    between-{ifelse(sims$resid_var, ' and within-', '')}subject variability,
    as well as uncertainty in population parameter estimates via
    sampling from the posterior distribution."
  )
  
}
```

### Model location

Define `modelName` and path to the model directory (`MODEL_DIR`).

```{r setup_bbr, echo = params$include_code, message = FALSE}
# Set directories for bbr models ----------------------------
MODEL_DIR <- params$modelDir
modelName <- params$run
thisModelPath <- file.path(MODEL_DIR, modelName)
```

### Figure location

If saving figures out to pdf, define where those pdfs should be saved to.
Here the figures are saved to ```deliv > figure > model_run_number```

```{r makeDir_mrggsave, echo = params$include_code, eval = params$run_mrggsave}
thisFigDir <- file.path(figDir, modelName)
if (!file.exists(thisFigDir)) dir.create(thisFigDir)

### set mrggsave figure directory here
options(mrggsave.dir = thisFigDir)

thisModelDir <- file.path(MODEL_DIR, params$run)


```


### Read output

Read in posterior samples from the `.ext` files. If available, also read in the
individual posteriors and objective function values for calculating shrinkage
and LOO-CV.  If individual posteriors are not available, calculated medians of
shrinkages reported by NONMEM instead.

```{r echo = params$include_code}
ext <- get_chain_files(MODEL_DIR, params$run, params$n_chains, "ext") %>% 
  filter(ITERATION > 0)

#TODO modify build_path_from_model to work with chains
fn_iph <- file.path(
  MODEL_DIR,
  params$run,
  glue("{params$run}_{params$n_chains}"),
  glue("{params$run}_{params$n_chains}.iph")
)
if (file.exists(fn_iph)) {
  
  iph <- get_chain_files(MODEL_DIR, params$run, params$n_chains, "iph") %>% 
    filter(ITERATION > 0)
  ipar <- iph %>% select(chain, ITERATION, ID, starts_with("ETA"))
  iobj <- iph %>% select(chain, ITERATION, ID, MCMCOBJ)
  
  # calculate shrinkage
  shk0 <- baysh(ipar, ext)
  
} else {
  
  shk0 <- get_chain_files(MODEL_DIR, params$run, params$n_chains, "shk") %>% 
    # From Intro to NM 7: "Type 4=%Eta shrinkage SD version"
    filter(TYPE == 4) %>% 
    select(starts_with("ETA")) %>% 
    summarise(across(.fns = median)) %>% 
    pivot_longer(everything(), names_to = "eta", values_to = "shrinkage")
  
}

shk <- shk0 %>% 
  mutate(
    shrinkage = sig(shrinkage),
    eta = str_extract(eta, "[\\d]+"),
    parameter = glue("OMEGA({eta},{eta})")
  ) %>% 
  select(-eta)

## Individual objective function values (log-likelihoods)
#fn_iobj <- file.path(
#  MODEL_DIR,
#  params$run,
#  glue("{params$run}_{params$n_chains}"),
#  "iobj.txt"
#)
#if (file.exists(fn_iobj)) {
#  iobj <- map(seq_len(params$n_chains), function(.chain) {
#    data.table::fread(
#      file = file.path(
#        MODEL_DIR,
#        params$run,
#        glue("{params$run}_{.chain}"),
#        "iobj.txt"
#      ),
#      header = FALSE
#    ) %>% 
#      as_tibble() %>% 
#      select(-1) %>% 
#      select_if(~ sum(.x) != 0)
#  })
#}

#data.table::fread(file = file.path(
#  MODEL_DIR,
#  params$run,
#  glue("{params$run}_{1}"),
#  "iobj.txt"),
#  header = FALSE
#) %>% 
#  names

```
  

# Model details

## 1st chain details

A summary of high-level model details using only output from the first chain.

Read in the model details using `read_model`. Details stored in the `mod` object
can be used to identify the location of the source data (used in $DATA) - to see
how this is done look at the `bbr::get_data_path()` and
`bbr::build_path_from_model()` helper functions.

```{r modelDetails, echo = params$include_code, results = "asis"}
mod <- read_model(
  file.path(MODEL_DIR, params$run, glue("{params$run}_1"))
)
mod
```

```{r modelOutputSummary, echo = params$include_code, results = "asis"}
sum <- mod %>% model_summary()
print(sum)
```

## Parameter estimates 

Compute summaries of posterior distributions (now using all `params$n_chains`
chains), as well as some diagnostics.

Bulk effective sample size (ESS) is a measure of sampling efficiency for the
location of the distribution, while Tail ESS is a measure of sampling efficiency
for the tails (5% and 95% quantiles) of the distribution. Higher values indicate
greater sampling efficiency.  A very rough rule of thumb is to aim for at least
400 for each parameter.

R-hat is a convergence diagnostic that compares the between- and within-chain
variances of model parameters. Values close to 1 indicate that the chains have
converged to similar distributions.  Aim for less than about 1.05 for all
parameters.




```{r paramEst, echo=FALSE}
n_theta <- length(sum$parameter_names$theta)
n_omega <- length(sum$parameter_names$omega)
n_sigma <- length(sum$parameter_names$sigma)

size_omega <- (-1 + sqrt(1 + 4*1*n_omega*2)) / 2
size_sigma <- (-1 + sqrt(1 + 4*1*n_sigma*2)) / 2

fix_diag <- tibble(
  parameter = sum$parameter_names %>% do.call(c, .),
  fixed = sum$parameters_data[[1]]$fixed %>% do.call(c, .) %>% as.logical,
  diag = c(rep(NA, n_theta), block(size_omega), block(size_sigma))
)

ext_tbl <- ext %>%
  filter(ITERATION > 0) %>%
  select(-ITERATION, -MCMCOBJ)
n_param <- ncol(ext_tbl) - 1  # don't include chain
n_iter <- max(ext$ITERATION)
param_array <- array(
  double(n_iter * params$n_chains * n_param),
  dim = c(n_iter, params$n_chains, n_param),
  dimnames = list(NULL, NULL, setdiff(names(ext_tbl), "chain"))
)
for (.chain in seq_len(params$n_chains)) {
  param_array[,.chain,] <- ext_tbl %>%
    filter(chain == .chain) %>%
    select(-chain) %>%
    as.matrix()
}

ptable <- rstan::monitor(param_array, warmup = 0, print = FALSE) %>%
  as.matrix %>%
  as.data.frame() %>%
  mutate(
    parameter = rownames(.)
    #mean_med_diff = (mean - `50%`) / `50%` * 100
  ) %>%
  mutate(across(c(-n_eff, -Bulk_ESS, -Tail_ESS, -valid, -parameter), sig)) %>%
  left_join(fix_diag) %>%
  filter(!fixed)
if (!params$tbl_offdiag) ptable <- ptable %>% filter(is.na(diag) | diag)
ptable %>%
  rename(pct2.5 = "2.5%", median = "50%", pct97.5 = "97.5%", Neff = "n_eff") %>%
  mutate(
    "95% CI" = glue("({pct2.5},{pct97.5})"),
  ) %>%
  select(parameter, mean, median, "95% CI", Bulk_ESS, Tail_ESS, Rhat) %>%
  left_join(shk, by = "parameter") %>%
  knitr::kable(caption = "Summary of model parameter estimates.") #%>%
  #kable_styling(bootstrap_options = "striped", full_width = F)
```

## LOO-CV

PSIS-LOO CV is leave-one-out (LOO) cross-validation for Bayesian models using
Pareto smoothed importance sampling (PSIS). This is used for model comparison,
similar to the -2LL objective function for non-Bayesian models.

```{r echo = params$include_code}
#if (file.exists(fn_iobj)) {
#  n_iter <- nrow(iobj2[[1]])
#  n_id <- ncol(iobj2[[1]])
#  iobj_array2 <- array(
#    double(n_iter * params$n_chains * n_id),
#    dim = c(n_iter, params$n_chains, n_id)
#  )
#  for (.chain in seq_len(params$n_chains)) {
#    iobj_array2[,.chain,] <- as.matrix(iobj2[[.chain]])
#  }
#  
#  rel_n_eff <- relative_eff(exp(iobj_array2))
#  loo(iobj_array2, r_eff = rel_n_eff, cores = 2)
#} else {
#  print("No iobj.txt files found, so LOO-CV was not calculated.")
#}

if (file.exists(fn_iph)) {
  n_iter <- max(iobj$ITERATION)
  n_id <- n_distinct(iobj$ID)
  iobj_array <- array(
    double(n_iter * params$n_chains * n_id),
    dim = c(n_iter, params$n_chains, n_id)
  )
  for (.chain in seq_len(params$n_chains)) {
    iobj_array[,.chain,] <- iobj %>% 
      filter(chain == .chain) %>% 
      arrange(ID, ITERATION) %>% 
      pull(MCMCOBJ) %>% 
      as.matrix()
  }
  
  rel_n_eff <- relative_eff(exp(iobj_array))
  loo(iobj_array, r_eff = rel_n_eff, cores = 2)
} else {
  print("No .iph files found, so LOO-CV was not calculated.")
}
```

# Load Spec

The aim is to use the information in the spec file to label the figures automatically.

```{r yspec_details, echo = params$include_code}
# Tell R where to find the yml
specLo <- here::here("data", "spec", params$yspec)

# load in the spec file
spec <- ys_load(specLo)
```


# Read in data

Model output (EPRED, IPRED, NPDE, EWRES, ETAs) is read in from either the output
of simulations (see `run-sims.R`) or from NONMEM output only.  When only NONMEM
output is used, medians of these values across all chains are calculated.

After reading in the NONMEM dataset and the output dataset they're joined by a
`NUM` column. **This assumes that a row number column (called `NUM`) was
included during data assembly.** The idea here is that in NONMEM, you table
just `NUM` and none of the other input data items. They all will get joined
back to the NONMEM output ... even character columns.

The `data` used in the diagnostic plots has been filtered to only include the
observations (i.e. `EVID==0`). Note that further modifications maybe needed, for
example, if BLQ data was included in the model or if the `DV` was
log-transformed. The dataset also converts the categorical covariates of
interest to factors using the `yspec_add_factors` function and details described
in the spec file.

The `id` subset gets the first record per ID. This would usually be the baseline
value but consider filtering on a baseline flag if available. Also, if the model
includes inter-occasion variability (IOV), the occasion variable should be
included within the `distinct` function.

```{r read_in_data, echo = params$include_code, message=FALSE}
# Get original dataset and NONMEM output using median table values
data0 <- data.table::fread(get_data_path(sum), na.strings = ".") %>% 
  as_tibble()
if (params$sims_output_path != "") {
# Use simulated values
  data0 <- left_join(sims$data, data0, by = "NUM")
} else {
# Use NONMEM output (median table values) for all
  tab <- get_chain_files(MODEL_DIR, params$run, params$n_chains, "tab",
                         .chain_in_name = FALSE) %>% 
    group_by(NUM) %>% 
    summarise(across(.fns = median)) %>% 
    select(-chain)
  
  # ### Included partab for ETAs - CHECK needed when simulations run correctly
  # partab <- get_par_chain_files(MODEL_DIR, params$run, params$n_chains, "tab",
  #                        .chain_in_name = FALSE) %>% 
  #   group_by(NUM) %>% 
  #   summarise(across(.fns = median)) %>% 
  #   select(-chain)
  
  keep1 <- c("NUM", setdiff(names(tab), names(data0)))
  # keep2 <- c("NUM", setdiff(names(partab), names(data0)))
  data0 <- left_join(tab[,keep1], data0, by = "NUM")
  # data0 <- left_join(partab[,keep2], data0, by = "NUM")

}

# filter to observation rows only
data <- data0 %>% 
  filter(EVID == 0) %>% 
  yspec_add_factors(spec, .suffix = "")

if(isTRUE(params$logDV)) {
  data <- mutate(data, 
                 LNPRED = PRED, 
                 PRED = exp(PRED),
  )  
}

# filter to single row per ID and include factors 
id <- distinct(data, ID, .keep_all = TRUE) 
```


# Convergence diagnostic plots

```{r echo = params$include_code}
ext_plot <- ext %>% 
  # thinning: take every nth sample
  filter(row_number() %% params$n_thin == 0) %>% 
  pivot_longer(-c(ITERATION, chain)) %>% 
  left_join(fix_diag %>% rename(name = parameter)) %>% 
  filter(!fixed)
if (!params$plot_offdiag) ext_plot <- ext_plot %>% filter(is.na(diag) | diag)
```

These plots assess whether all of the chains have converged to a single,
stationary distribution.

## Trace and density plots

```{r trace_density_plots, echo = params$include_code, message=FALSE}
p <- map(unique(ext_plot$name), function(.x) {
  # print(.x)
  df <- ext_plot %>%
    filter(name == .x) %>% 
    select(ITERATION, chain, value)
  if (min(df$value) == max(df$value)) {
    return(NULL)
  }
  p1 <- ggplot(df, aes(ITERATION, value, colour = factor(chain))) +
    geom_line() +
    labs(x = "Iteration", y = "Estimate", colour = "Chain")
  p2 <- ggplot(df, aes(value, colour = factor(chain))) +
    geom_density() +
    labs(x = "Estimate", y = "Density", colour = "Chain")
  # p3 <- ggplot(df, aes(value)) +
  #   geom_density() +
  #   labs(x = "Estimate", y = "Density")
  p0 <- p1 / p2 + plot_annotation(.x)
  return(p0)
}) %>% 
  purrr::compact() # remove NULL elements of list

pDensity = p
```

```{r include_trace_density, eval=params$include_plots, include=params$include_plots, echo=F, message=FALSE}
p
```

```{r save_trace_density, include = FALSE, eval = params$run_mrggsave, message=FALSE}
mrggsave(
  p,
  params$script, 
  stem = c(params$run, "trace-density"),
  dir = thisFigDir,
  width = 5,
  height = 7
)
```

```{r rm_trace_density, include=F}
rm(p)
```

## Pairs

Look for any strong correlation between parameters, indicating possible
over-parameterisation.

```{r param_pairs_plots, echo = params$include_code, message=FALSE}
ext_pairs <- ext_plot %>% 
  select(-fixed, -diag) %>% 
  pivot_wider(names_from = "name", values_from = "value") %>% 
  # further thinning: take every nth sample again
  filter(row_number() %% params$n_thin2 == 0)

names_theta <- str_subset(names(ext_pairs), "^THETA")
if (is.null(params$theta_cov)) {
  names_fixed_noncov <- names_theta
} else {
  names_fixed_cov <- intersect(
    names(ext_pairs),
    paste0("THETA", params$theta_cov)
  )
  names_fixed_noncov <- setdiff(names_theta, names_fixed_cov)
}
names_random <- names(ext_pairs) %>%
  str_subset("^OMEGA|^SIGMA") %>% 
  # pairs_plot() doesn't like names with parentheses without this format
  str_replace("(.*)", "\\1 // \\1")

p_fixed_noncov <- ext_pairs %>% 
  pairs_plot(names_fixed_noncov, progress = FALSE) +
  rot_x(45)
p_random <- ext_pairs %>% pairs_plot(names_random)+
  rot_x(45)

if (!is.null(params$theta_cov)) {
  p_fixed_cov <- ext_pairs %>% pairs_plot(names_fixed_cov, progress = FALSE)+
  rot_x(45)
}
```

```{r include_param_pairs, eval=params$include_plots, include=params$include_plots, echo=F, message=FALSE, fig.width=9, fig.height=9}
p_fixed_noncov
if (!is.null(params$theta_cov)) p_fixed_cov
p_random
```

```{r save_param_pairs, include = FALSE, eval = params$run_mrggsave, message=FALSE}
mrggsave(
  p_fixed_noncov,
  params$script, 
  stem = c(params$run, "pairs-fixed-noncov"),
  dir = thisFigDir,
  width = 9,
  height = 9
)
if (!is.null(params$theta_cov)) {
  mrggsave(
    p_fixed_cov,
    params$script, 
    stem = c(params$run, "pairs-fixed-cov"),
    dir = thisFigDir,
    width = 9,
    height = 9
  )
}
mrggsave(
  p_random,
  params$script, 
  stem = c(params$run, "pairs-random"),
  dir = thisFigDir,
  width = 9,
  height = 9
)
```

```{r rm_param_pairs, include=F}
rm(p_fixed_noncov, p_random)
if (!is.null(params$theta_cov)) rm(p_fixed_cov)
```

## ESS vs sample

Plots Bulk and Tail ESS versus iteration to check that ESS increases linearly.

```{r ess_vs_sample_plots, echo = params$include_code, message=FALSE}
p0 <- map(unique(ext_plot$name), function(.x) {
  plot_change_ess(param_array, .x)
}) %>% 
  purrr::compact() # remove NULL elements of list

pESSsample = p0

p <- map(1:length(unique(ext_plot$name)), function(.x) {
  p0[[.x]] + plot_annotation((unique(ext_plot$name))[.x])
}) 

```

```{r include_ess_vs_sample_plots, eval=params$include_plots, include=params$include_plots, echo=F, message=FALSE}
p
```

```{r save_ess_vs_sample_plots, include = FALSE, eval = params$run_mrggsave, message=FALSE}
mrggsave(
  p,
  params$script, 
  stem = c(params$run, "ess-vs-sample"),
  dir = thisFigDir,
  width = 5,
  height = 5
)
```

```{r rm_ess_vs_sample, include=F}
rm(p, p0)
```

## ESS vs quantile

Plots Bulk and Tail ESS versus quantile to better diagnose areas of the
distributions that the iterative algorithm fails to explore efficiently.

```{r ess_vs_quantile_plots, echo = params$include_code, message=FALSE}
p0 <- map(unique(ext_plot$name), function(.x) {
  plot_quantile_ess(param_array, .x)
}) #%>% 
  #purrr::compact() # remove NULL elements of list

pESSquantile = p0

p <- map(1:length(unique(ext_plot$name)), function(.x) {
  p0[[.x]] + plot_annotation((unique(ext_plot$name))[.x])
}) 


```

```{r include_ess_vs_quantile_plots, eval=params$include_plots, include=params$include_plots, echo=F, message=FALSE}
p
```

```{r save_ess_vs_quantile_plots, include = FALSE, eval = params$run_mrggsave, message=FALSE}
mrggsave(
  p,
  params$script, 
  stem = c(params$run, "ess-vs-quantile"),
  dir = thisFigDir,
  width = 5,
  height = 5
)
```

```{r rm_ess_vs_quantile, include=F}
rm(p, p0)
```



```{r save_combine_convergence_plots, include = FALSE, eval = params$run_mrggsave, message=FALSE}

# combine density and ess plots for report

p <- map(seq(1, length(unique(ext_plot$name))), function(.x) {
  p0 <- pDensity[[.x]] | (pESSsample[[.x]] / pESSquantile[[.x]]) 
  p0 = p0 + plot_annotation(
  title = unique(ext_plot$name)[.x])
  return(p0)
}) #%>% 
  #purrr::compact()

mrggsave(
  p,
  params$script, 
  stem = c(params$run, "convergence"),
  dir = thisFigDir,
  width = 8,
  height = 5
)

rm(p, pESSsample, pESSquantile, pDensity)
```


# General diagnostic plots

The following plots assume that the preferred x-axis labels are defined here. 

```{r xAxis_label_names, echo = params$include_code}
### Ideally get units from yaml

xTIME <- "TIME //Time (h)"
#xTAD <- "TAD //Time after dose (h)"
xPRED <-  "EPRED //Population predicted concentration"
yEWRES <-  "EWRES //Expected weighted residual"
yNPDE <-  "NPDE //Normalized prediction distribution error"
```

## DV vs population and individual predictions

Create plots of DV vs population and individual predictions for the full dataset
and stratified by renal function and hepatic function.

```{r DV_PRED_plots, echo = params$include_code, message=FALSE}
# DV vs population predictions
if (params$plot_ci & !is.na(params$sims_output_path)) {
  dvp <- dv_pred_ci(
    data,
    x = "EPRED//Population predicted {xname}",
    x_lo = "EPRED_lo",
    x_hi = "EPRED_hi"
  )
} else {
  dvp <- dv_pred(data, x = "EPRED//Population predicted {xname}")
}
  
# DV vs individual predictions
if (params$plot_ci & !is.na(params$sims_output_path) &
    "IPRED_lo" %in% names(data)) {
  dvip <- dv_pred_ci(
    data,
    x = "IPRED//Individual predicted {xname}",
    x_lo = "IPRED_lo",
    x_hi = "IPRED_hi"
  )
} else {
  dvip <- dv_ipred(data, x = "IPRED//Individual predicted {xname}")
}

p <- pm_grid(list(dvp, dvip), nrow = 2, ncol = 1)
```

```{r results="asis", include=params$include_plots, echo=F}
dv_pred_text
```

```{r include_DV_PRED, include=params$include_plots, echo=F, message=FALSE}
p
```


```{r save_DV_PRED, include = FALSE, eval = params$run_mrggsave, message=FALSE}
mrggsave(
  p,
  params$script, 
  stem = c(params$run, "dv-pred-ipred"),
  dir = thisFigDir,
  width = 5,
  height = 7
)
```

```{r rm_dv_pred, include=F}
rm(p, dvp, dvip)
```


## NPDE plots

```{r results="asis", include=params$include_plots, echo=F}
npde_text
```

NPDE vs population predictions, time and time after dose.

```{r results="asis", include=params$include_plots, echo=F}
pop_pred_text
```

```{r NPDE_plots, echo = params$include_code, message = FALSE}
##' Plan to display these three plots in a single, 3 panel figure and so the y-axis
##' labels are removed manually for display purposes
p1 <- npde_pred(data, x = xPRED, y = "NPDE //  ")
p2 <- npde_time(data, x = xTIME)
#p3 <- npde_tad(data, x = xTAD, y = "NPDE //  ")

p <- pm_grid(list(p1, p2), nrow = 3, ncol = 1) 

```

```{r include_NPDE, eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE, fig.height = 7}
p
```

```{r save_NPDE, include = FALSE, eval = params$run_mrggsave, message = FALSE}
mrggsave(
  p,
  stem = c(params$run, "npde-pred-time-tad"),
  width = 5,
  height = 7
)
```

```{r rm2, include = F}
rm(p)
```


NPDE vs continuous covariates

```{r NPDE_cont_cov_plots, echo = params$include_code, message = FALSE}
NPDEco <- spec %>% 
  ys_select(params$contCov) %>%   # select the covariates of interest
  axis_col_labs(title_case = TRUE,  # converts yspec short to title_case 
                short_max = 20)     # if yspec short is >10 characters it keeps the abbreviation

p1 <- npde_cont(data, x = NPDEco[1])
#p2 <- npde_cont(data, x = NPDEco[2])
#p3 <- npde_cont(data, x = NPDEco[3])

p <- pm_grid(list(p1), ncol = 1) 
```

```{r include_NPDE_cont_cov, eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE, fig.height = 7}
p
```

```{r save_NPDE_cont_cov, include = FALSE, eval = params$run_mrggsave, message = FALSE}
mrggsave(
  p,
  stem = c(params$run, "npde-cont-cov"),
  width = 5,
  height = 7
)
```

```{r rm2_cont_cov, include = F}
rm(p)
```

NPDE vs categorical covariates.

```{r NPDE_cat_cov_plots, echo = params$include_code, message = FALSE}
NPDEca <- spec %>% 
  ys_select(params$catCov) %>%   # select the covariates of interest
  axis_col_labs(title_case = TRUE)  # converts yspec short to title_case 

p1 <- npde_cat(data, x = NPDEca[1])
#p2 <- npde_cat(data, x = NPDEca[2]) +rot_x(45)

p <- pm_grid(list(p1), nrow = 2, ncol = 1) 

```

```{r include_NPDE_cat_cov, eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE}
p
```

```{r save_NPDE_cat_cov, include = FALSE, eval = params$run_mrggsave, message = FALSE}
mrggsave(
  p,
  stem = c(params$run, "npde-cat-cov"),
  width = 5,
  height = 7
)
```

```{r rm2_cat_cov, include = F}
rm(p)
```


## NPDE density histogram

```{r npde_hist_plots, echo = params$include_code, message = FALSE}
p <- npde_hist(data)
```

```{r include_npde_hist, eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE}
p
```

```{r save_npde_hist, include = FALSE, eval = params$run_mrggsave, message = FALSE}
mrggsave(
  p,
  stem = c(params$run, "npde-hist"),
  width = 5,
  height = 5
)
```

```{r rm3, include = F}
rm(p)
```

## EWRES vs population predictions, time and time after dose

```{r results="asis", include=params$include_plots, echo=F}
ewres_text
```

```{r results="asis", include=params$include_plots, echo=F}
pop_pred_text
```

```{r ewres_plots, echo = params$include_code, message=FALSE}
p_ewres_epred <- res_pred(data, x = xPRED, y = yEWRES)
p_ewres_time <-  res_pred(data, x = xTIME, y = yEWRES)
#p_ewres_tad <-   res_pred(data, x = xTAD, y = yEWRES)
p <- pm_grid(
  list(
    p_ewres_epred,
    p_ewres_time
  ),
  nrow = 3,
  ncol = 1
)
```

```{r include_ewres, eval=params$include_plots, include=params$include_plots, echo=F, message=FALSE, fig.height = 7}
p
```

```{r save_ewres, include = FALSE, eval = params$run_mrggsave, message=FALSE}
mrggsave(
  p,
  params$script, 
  stem = c(params$run, "ewres-epred-time-tad"),
  dir = thisFigDir,
  width = 5,
  height = 7
)
```

```{r rm_ewres_plots, include=F}
rm(p)
```



## EWRES qq and density plot

```{r ewres_qq_density_plots, echo = params$include_code, message=FALSE}
p_ewres_q <- wres_q(data, "EWRES")
p_ewres_hist <- cont_hist(data, "EWRES", y = "..density..")
p <- pm_grid(list(p_ewres_q, p_ewres_hist), nrow = 2, ncol = 1)
```

```{r include_ewres_qq_density, eval=params$include_plots, include=params$include_plots, echo=F, message=FALSE}
p
```

```{r save_ewres_qq_density, include = FALSE, eval = params$run_mrggsave, message=FALSE}
mrggsave(
  p,
  params$script, 
  stem = c(params$run, "ewres-qq-hist"),
  dir = thisFigDir,
  width = 5,
  height = 7
)
```

```{r rm_ewres_qq_density, include=F}
rm(p)
```



# EBEs-based diagnostics

```{r results="asis", include=params$include_plots, echo=F}
etas_text
```



## ETA pairs plot 

```{r eta_pairs_plots, echo = params$include_code, message = FALSE}
p <- eta_pairs(id, params$etas)
```

```{r include_eta_pairs, eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE}
p
```

```{r save_eta_pairs, include = FALSE, eval = params$run_mrggsave, message = FALSE}
mrggsave(
  p,
  stem = c(params$run, "eta", "pairs"),
  width = 5,
  height = 5
)
```

```{r rm5, include = F}
rm(p)
```





## Continuous covariate plots

These plots uses the yspec to automatically rename the axis labels.

```{r get_cont_cov_labels, echo = params$include_code, eval = params$run_mrggsave}
co <- spec %>% 
  ys_select(params$contCov) %>%     # select the covariates of interest
  axis_col_labs(title_case = TRUE,  # converts yspec short to title_case 
                short_max = 20)     # if yspec short is >10 characters it keeps the abbreviation
```

### ETA vs continous covariates

Note that here we use a function that maps over the ETAs (not the covariates)
because the purpose of these plots was to determine whether there were any
trends in the covariates for a given ETA. This may need to be edited to address
different study specific questions

```{r eta_vs_cont_plots, echo = params$include_code, message = FALSE}
p <- purrr::map(.x = params$etas, ~ map_wrap_eta_cont(.x, co, id, .ncol=1))
```

```{r include_eta_vs_cont, eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE}
p
```

```{r save_eta_vs_cont, include = FALSE, eval = params$run_mrggsave, message = FALSE}
mrggsave(
  p,
  stem = c(params$run, "eta-all", "cont", "cov"),
  width = 5,
  height = 5
)
```

```{r rm6, include = F}
rm(p)
```

### Continous covariate pairs plot

```{r contCov_pairs_plots, echo = params$include_code, message = FALSE}
# need to manually force units onto a new line for EGFR here to fit label in the panel
# if ("BLEGFR" %in% params$contCov) {
#   co2 <- co
#   co2[which(names(co2) == "BLEGFR")] = "BLEGFR//Estimated GFR \n(ml/min/1.73m2)"
# }

co2 <- str_replace(co, "\\(", "\n(")
p <- eta_pairs(id, co2) + rot_x(45)
```

```{r include_contCov_pairs, eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE}
p
```

```{r save_contCov_pairs, include = FALSE, eval = params$run_mrggsave, message = FALSE}
mrggsave(
  p,
  stem = c(params$run, "eta", "all", "contCov", "pairs"),
  width = 5,
  height = 6
)
```

```{r rm7, include = F}
rm(p)
```


## Categorical covariate plots

These plots uses the yspec to automatically rename the axis labels.

```{r get_cat_cov_labels, echo = params$include_code, eval = params$run_mrggsave}
ca <- spec %>% 
  ys_select(params$catCov) %>%   # select the covariates of interest
  axis_col_labs(title_case = TRUE)  # converts yspec short to title_case 
```


### ETA vs categorical covariates

Note that here we use a function that maps over the covariates (not the ETAs)
because the purpose of these plots was to determine whether there is any
difference in the distribution of ETAs across studies, dosing groups and disease
states. This should be updated to reflect the questions you're trying to
address.


```{r eta_vs_cat_plots, echo = params$include_code, message = FALSE}
if (length(params$etas) > 1) {
  p <- purrr::map(.x = ca, ~ map_eta_cat(.x, params$etas, id)) 
} else {
  ## CHECK: depending on the labels, this may need to be changed 
  p <- purrr::map(.x = ca, ~ eta_cat(id, .x, params$etas) + rot_x(35))
}

pList <- pm_grid(list(p[[1]], p[[2]]), nrow = 2, ncol = 1) 

```

```{r include_eta_vs_cat, eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE}
p
```

```{r save_eta_vs_cat, include = FALSE, eval = params$run_mrggsave, message = FALSE}
## As of mrggsave v0.4.0, if you pass mrggsave a named list of plots, it will use this to
## name the plots that it writes out (regardless of whether stem is defined). 
## If you don't want to use this feature, you can pass unname(p), instead of just p
mrggsave(
  list(pList, unname(p)),
  stem = c(params$run, "eta", "all", "cat", "cov"),
  width = 5,
  height = 7
)
```


# Session details

It is considered good practice to include these details at the end of all rmd scripts

```{r details, include = TRUE}
Sys.getenv("AMI_NAME")
sessioninfo::session_info()
bbr::bbi_version()
```


